Comparison of Catalogs

### 2024-07-29 compare/compare.qmd
Inclination

## Inclanation

```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```

```{python}
dt["INCL"].mask
```
```{python}
dt["diff_inc"] = relative_diff(hec = dt["INCL"],lcv = dt["inc"])
percent_desc_histogram(dt["diff_inc"])
```

```{python}
#k = sigma_clip(dt["diff_inc"])
dt["diff_T"].info
```

>>>>

## Inclination

```{python}
temp = dt[["inc", "INCL"]].to_pandas()

sns.histplot(temp[["inc", "INCL"]], kde = True)
plt.xlabel("Inclination of galaxies [deg]")
plt.show()

temp["Percentage Change [%]"] = (-temp["inc"] + temp["INCL"])/temp["INCL"]
temp.loc[np.isinf(temp["Percentage Change [%]"]), "Percentage Change [%]"] = np.nan
sns.histplot(temp["Percentage Change [%]"], kde = True)
plt.show()
temp.describe()
```

We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LCV inclination are higher. However, since their means, median, min and maxes are similar and the percentage change is practically 0% (mean, median, $\sigma$ = 0 with a range $[-3\%,1\%]$), we can ignore the differences and assume they are the same values.
